Funding programmes for early career researchers marginally improves their collaboration independence, but not cognitive independence

### 2023-10-25 article.Rmd
small changes in text

We also tested an assumption that had a hope of reducing time intensity of data collection by substitution it for algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors. Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about XXXXX % of cases (see the Attachment 1).

@@

However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
$$RII = ((1- I1) + I2 + I3 + I4) / 4$$ 
since the previous formula had a small error (it weighted I4 double,, i.e. 2*I4). In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method. Initially, we conducted a random sampling of 1200 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications. Then we  compiled all publications generated by the researchers within our sample and their respective supervisors. We then calculated the posterior distribution of topics for this compilation, employing a pre-trained topic model. This way we wanted to mitigate the endogeneity of the topic modelling which would be stronger if we calculated topic model directly on the publications of our sample researchers.

To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Results -> Descriptives -> Missing data).

>>>>

We also tested an assumption that had a hope of reducing time intensity of data collection by substitution it for algorithmic approach: using the "most frequent co-author of the first 5 publications" as a proxy to identify supervisors. Crosschecking this proxy with the actual data about supervisors we found manually, we found that this algorithm was able to identify supervisors correctly in about 56 % of cases (see the Attachment 1).

@@

However, we have made some changes to the indicator. After consulting with its authors, we have changed the aggregation formula to 
$$RII = ((1- I1) + I2 + I3 + I4) / 4$$ 
since the previous formula had a small error (it weighted I4 double,, i.e. 2*I4). In determining the proportion of a researcher's own research topics (I4), we opted for text-based topic modeling utilizing publication titles and abstracts, diverging from the originally suggested bibliographic coupling method. Initially, we conducted a random sampling of 3000 publications from a set of all publications produced by researchers affiliated with Czech institutions as cataloged in the RIV database, estimated number of topics using Griffiths2004 indicator and calculated LDA topic model on this set of publications. Then we  compiled all publications generated by the researchers within our sample and their respective supervisors. We then calculated the posterior distribution of topics for this compilation, employing a pre-trained topic model. This way we wanted to mitigate the endogeneity of the topic modelling which would be stronger if we calculated topic model directly on the publications of our sample researchers.

To calculate this indicator, we required at least 3 publications. This led to an increased number of missing observations (see section Descriptives -> Missing data).
